Extended Data

### 2021-11-18 doc/manuscript/Dow_manuscript_Nature.Rmd
fix author affiliation order
one-word change to make statement technically correct
Zohner study looks at temperate deciduous species over > 1 year, so "forests" is appropriate here.

Cameron Dow^1,11^ ( Orcid ID : 0000-0002-8365-598X)

Albert Y. Kim^1,2^ ( Orcid ID : 0000-0001-7824-306X)

Loïc D’Orangeville^3,4^ ( Orcid ID : 0000-0001-7841-7082)

@@

Grant L. Harley^5^ ( Orcid ID : 0000-0003-1557-8465)

Justin T. Maxwell^6^ (Orcid ID: 0000-0001-9195-3146)

Ian R. McGregor^1,7^ (Orcid ID: 0000-0002-5763-021X)

@@

Sean McMahon^8,10^ (Orcid ID : 0000-0001-8302-6908)

Neil Pederson^3^ (Orcid ID : 0000-0003-3830-263X)

Alan J. Tepley^1,9^ ( Orcid ID : 0000-0002-5701-9613)

Kristina J. Anderson-Teixeira^1,10^* ( Orcid ID : 0000-0001-8461-9713)

@@

2. Statistical & Data Sciences; Smith College; Northampton, MA 01063, USA

3. Harvard Forest, Petersham, MA 01366, USA

4. Faculty of Forestry and Environmental Management, University of New Brunswick, Fredericton, NB, E3B 5A3, Canada.

5. Department of Earth and Spatial Sciences, University of Idaho, ID 83844, USA

6. Department of Geography, Indiana University, Bloomington, IN 47405, USA

7. Center for Geospatial Analytics; North Carolina State University; Raleigh, NC 27607, USA

8. Smithsonian Environmental Research Center, Edgewater, MD, USA

9. Canadian Forest Service, Northern Forestry Centre, Edmonton, Alberta, Canada

10. Forest Global Earth Observatory; Smithsonian Tropical Research Institute; Panama, Republic of Panama

11. Department of Forestry and Natural Resources, Purdue University, West Lafayette, Indiana, USA

@@

While responses of leaf phenology and seasonal _NEE_ to warming spring temperatures have been documented[@jeong_phenology_2011; @keenan_net_2014; @buermann_widespread_2018; @ibanez_forecasting_2010; @menzel_european_2006; @menzel_growing_1999;@finzi_carbon_2020], little is known about how the longest-lived component of fixed C in trees, the woody growth, is responding to warming spring temperatures. 
In fact, we are aware of only one study that has documented stem-growth phenology of temperate deciduous species over multiple years[@dorangeville_peak_2021]. <!-- I'm not aware of any others, but we do want to make sure we're not missing anything. klesse_integrating_2016 and martin_hydrometeorology_2017 both do this, but for conifers.-->
The climate sensitivity of woody growth phenology in temperate deciduous trees and its link to annual growth has never been studied *in-situ* (but see Ref.[@zohner_how_2021] for a controlled sapling experiment).

>>>>

Cameron Dow^1,2^ ( Orcid ID : 0000-0002-8365-598X)

Albert Y. Kim^1,3^ ( Orcid ID : 0000-0001-7824-306X)

Loïc D’Orangeville^4,5^ ( Orcid ID : 0000-0001-7841-7082)

@@

Grant L. Harley^6^ ( Orcid ID : 0000-0003-1557-8465)

Justin T. Maxwell^7^ (Orcid ID: 0000-0001-9195-3146)

Ian R. McGregor^1,8^ (Orcid ID: 0000-0002-5763-021X)

@@

Sean McMahon^9,11^ (Orcid ID : 0000-0001-8302-6908)

Neil Pederson^4^ (Orcid ID : 0000-0003-3830-263X)

Alan J. Tepley^1,10^ ( Orcid ID : 0000-0002-5701-9613)

Kristina J. Anderson-Teixeira^1,11^* ( Orcid ID : 0000-0001-8461-9713)

@@

2. Department of Forestry and Natural Resources, Purdue University, West Lafayette, Indiana, USA

3. Statistical & Data Sciences; Smith College; Northampton, MA 01063, USA

4. Harvard Forest, Petersham, MA 01366, USA

5. Faculty of Forestry and Environmental Management, University of New Brunswick, Fredericton, NB, E3B 5A3, Canada.

6. Department of Earth and Spatial Sciences, University of Idaho, ID 83844, USA

7. Department of Geography, Indiana University, Bloomington, IN 47405, USA

8. Center for Geospatial Analytics; North Carolina State University; Raleigh, NC 27607, USA

9. Smithsonian Environmental Research Center, Edgewater, MD, USA

10. Canadian Forest Service, Northern Forestry Centre, Edmonton, Alberta, Canada

11. Forest Global Earth Observatory; Smithsonian Tropical Research Institute; Panama, Republic of Panama

@@

While responses of leaf phenology and seasonal _NEE_ to warming spring temperatures have been documented[@jeong_phenology_2011; @keenan_net_2014; @buermann_widespread_2018; @ibanez_forecasting_2010; @menzel_european_2006; @menzel_growing_1999;@finzi_carbon_2020], little is known about how the longest-lived component of fixed C in trees, the woody growth, is responding to warming spring temperatures. 
In fact, we are aware of only one study that has documented stem-growth phenology of temperate deciduous forests over multiple years[@dorangeville_peak_2021]. <!-- I'm not aware of any others, but we do want to make sure we're not missing anything. klesse_integrating_2016 and martin_hydrometeorology_2017 both do this, but for conifers.-->
The climate sensitivity of woody growth phenology in temperate deciduous trees and its link to annual growth has never been studied *in-situ* (but see Ref.[@zohner_how_2021] for a controlled sapling experiment).
